%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
    {\Huge \scshape Anshu Kumar Singh} \\ \vspace{1pt}
    Bangalore, Karnataka 560062 \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ 8757452804 ~ \href{mailto:anshu0157@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{anshu0157@gmail.com}} ~ 
    \href{https://www.linkedin.com/in/alpha9-falcon/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/anshu}}  ~
    \href{https://github.com/anshu0157}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/anshu0157}}
    \vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Noida Institute of Engineering and Technology}{August 2017 -- May 2021}
      {B.Tech, Information Technology}{Greater Noida, Uttar Pradesh}
    
    \resumeSubheading
      {Sri Chaitanya Techno School}{March 2015 -- March 2017}
      {Class XII, CBSE (Science)}{Vishakhapatnam, Andhra Pradesh}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Kreditbee}{Dec. 2021 -- Present}
      {Software Engineer}{Bangalore, Karnataka}
      \resumeItemListStart
        \resumeItem{Formulated novel compliance regulations for VKYC, edRekyc, and NACH.}
        \resumeItem{Engineered new web services to streamline the loan process.}
        \resumeItem{Implemented a cron job to clear pending loan data and compute essential scores required for loan approval.}
        \resumeItem{Addressed 100+ customer issues and assisted in automating the loan process.}
        \resumeItem{\textbf{Tech Stack:}{ Python, Flask, Django, MySQL, AWS lambda, EC2, Bash script}}
      \resumeItemListEnd
        

    \resumeSubheading
      {QA InfoTech}{June 2021 -- Nov. 2021}
      {Software Engineer Trainee}{Noida, Uttar Pradesh}
      \resumeItemListStart
        \resumeItem{Engaged in automation testing as a Software Engineer Trainee, demonstrating proficiency in testing principles and methodologies.}
        \resumeItem{Contributed to test planning, design, and execution, ensuring thorough functional and regression testing coverage.}
        \resumeItem{Applied proactive troubleshooting, enhancing software stability and reliability.}
        \resumeItem{\textbf{Tech Stack:}{ Java, Selenium, MySQL}}
    \resumeItemListEnd

    \resumeSubheading
      {Codejudge}{Feb. 2021 -- April 2021}
      {Problem setter Intern}{Noida, Uttar Pradesh}
      \resumeItemListStart
        \resumeItem{Developed programming problems for CodeJudge's platform, ensuring clarity and relevance.}
        \resumeItem{Created comprehensive problem statements, test cases, and sample solutions.}
        \resumeItem{Reviewed user submissions, provided feedback, and resolved queries.}
        \resumeItem{\textbf{Tech Stack:}{ Python, Java, C++, JavaScript, SQL}}
    \resumeItemListEnd
    
  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Django Chat Application} $|$ \emph{Django, Python, HTML/CSS, JavaScript}}{May 2022}
          \resumeItemListStart
            \resumeItem{Designed and implemented the database schema using Django ORM for storing user information and chat messages.}
            \resumeItem{Developed user authentication and authorization functionality to ensure secure access to the chat application.}
          \resumeItemListEnd
          \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{Django E-commerce Website} $|$ \emph{Django, Python, HTML/CSS, JavaScript}}{Sept. 2021}
          \resumeItemListStart
            \resumeItem{Designed and implemented Django ORM database schema for optimized data management.}
            \resumeItem{Engineered user authentication and registration systems for secure account management.}
            \resumeItem{Created dynamic product catalog with search, filter, and sorting capabilities.}
            \resumeItem{Deployed platform on cloud hosting services for scalability and reliability.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-15pt}


%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, Java, C, HTML/CSS, JavaScript, SQL, Bash Script} \\
     \textbf{Cloud Services}{: AWS EC2, AWS Lambda, SNS/SQS, API Gateway, AWS ECS, CloudWatch, AWS Fargate, AWS ELB} \\
     \textbf{Technologies/Frameworks}{: Linux, Git, Flask, Django, Nginx, uwsgi/Gunicorn, Redis Lock, Celery, Rest API} \\
    }}
 \end{itemize}
 \vspace{-16pt}

%-----------INVOLVEMENT---------------
\section{Leadership / Extracurricular}
    \resumeSubHeadingListStart
        \resumeSubheading{REWA}{Sept. 2023 -- Dec. 2023}{Module lead}{Kreditbee}
            \resumeItemListStart
                \resumeItem{Led a team of 3 members in FCU project.}
                \resumeItem{Oversaw project planning, delegation of tasks, and timeline management.}
                \resumeItem{Facilitated team meetings, provided guidance, and resolved conflicts to ensure project success.}
            \resumeItemListEnd
    \resumeSubHeadingListEnd


\end{document}
